Refining from the VHDL-AMS Hardware Description Language to the BON High-level Specification Language

### 2009-09-13 papers/BON_VHDL/paper.tex
finalisation

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\ent}{\emph{entity}\xspace}
\newcommand{\arch}{\emph{architecture}\xspace}
\newcommand{\archs}{\emph{architectures}\xspace}
\newcommand{\inv}{\emph{invariant}\xspace}
\newcommand{\undef}{\emph{undefined}\xspace}
\newcommand{\arcoss}{\emph{across}\xspace}
\newcommand{\through}{\emph{through}\xspace}
%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

\title{Refining from the BON High-level Specification Language to the
  VHDL-AMS Hardware Description Language}

@@

%======================================================================
\section{Introduction}
\label{sec:introduction}
The \ST sensor platform, represents heterogeneous collection of digital, analog
and mixed signal hardware circuits. Embedded system complexity
requires the need to strive for formal descriptions each component
separately in order to produce specification of the \STS.
Our aim is to be able to describe the structures of circuits,
the behavior of circuits and the formal link between structures and behaviors.
In other words, the behavioral specification of the \STS may be
represented as a \inv on the signals at the circuit's ports and may be obtained
by taking the conjunction of the \emph{invariants} that describe
behaviors of the individual components separately.
For this purpose we need  sophisticated tool and methodology
in order to be able to achieve this goal. 
The authors will illustrate in this article how BON can represent a high
level analogue mapping and will further illustrate a procedure for
transformation from VHDL-AMS to BON.\\
This article provides two main contributions.
\begin{enumerate}
\item
 It provides a solution how to formally emulate
 piece of hardware using BON-JML approach; up to date BON and JML
 have been used mostly in the pure object oriented software construction.   
\item
It relates hardware description code and refinement.
This means that if there  is a code that is "correct by construction",
then it will be derivable from BON (informal/formal) specification to 
JML implementation.
\end{enumerate}
The rest of this article is organized as follows.
In \autoref{sec:vhdlams} we have  presented an overview of VHDL-AMS language.
\autoref{sec:choiceobon} defines  BON principles and explains the
reasons why we have decided to use BON method.
In \autoref{sec:mappingVB} we will show mapping between VHDL-AMS and BON.
A comprehensive list of the mapping between BON and VHDL-AMS can be
found in the appendix. 
The central part of the our article is \autoref{sec:refVB}, in which
we will give practical aspect of refinement , applied on 
first order passive RC Low-Pass filter, in order to produce formal 
specification and software simulation.\\ 
%=====================================================================

\section{VHDL-AMS}
\label{sec:vhdlams}
IEEE VHDL-AMS 1076.1 is the industry standard mixed-signal
high-level description language for electronic and multi-domain
systems. VHDL-AMS, as an superset of VHDL, supports modeling and
simulation of analog and mixed-signal systems. The main contribution
of VHDL-AMS is ability to describe the behaviour of complex system
trought differential and algebraic equations (DAEs). For this purpose,
VHDL-AMS introduces the following capabilities and therms:

\begin{itemize}
\item
\emph{Terminals} represents phisical connection points or circuit nodes
of a network connectivity. They are declared to be of various
\emph{natures}, which represent different energy domains of a system.
Terminals hold no values; their only role is to facilitate the formation
of conservative equation sets that, in turn, constrain the associated
\emph{branch quatities}.
\item
The \emph{quantities} denote a waveform or a time series of values.
The behaviour of the \emph{quantities} is given by the \emph{simultaneous
 statements}. They take values as a result of solving the set of simultaneous
ordinary differential and algebraic equations (DAEs). To simplify,
quantities can be understood as analog unknowns of (DAEs) that specify
analog behaviour. There are three kinds of quantity in VHDL-AMS: free,
branch and source quantities. A \emph{free quantity} can be used in
signal-flow modeling. A \emph{branch quantity} is used to model conservative energy
systems. A \emph{source quantity} is used for frequency and noise modeling.
\item
The \emph{simultaneous statements} creates one or more characteristic
equations that are solved by the dedicated simulation kernel a.k.a.
"analog solver", to model continuously valued behaviour. 
\item
The \emph{procedural statements} or \emph{procedural} express analog behaviour
using sequential statements. Actually procedural describes analog behaviour
by computing new values for quantities from the current value of quantities.
\item
The \emph{break statement} is an construct which allows to
initialize the DAE system at the beginning of a transient
simulation and to mark discontinuities during such a transient
simulation. For any concurrent break statement there is an associated process.
A break statement allows restart of the analog kernel,
than overrides quantity values and executes concurrently with the analogue model.

@@

for object-oriented systems  which emphasizes \emph{seamlessness},\xspace

@@

throughout the software lifecycle. Reversibility is the support for

@@

In VHDL-AMS, modelling represents an continious top-down-bottom-up

@@

models consistent with the code. Keeping in sync various models, documetation

@@

\emph{Seamlessness} also plays an important role in relating behaviours at

@@

general behaviour (\inv) and using existential quantification (\texttt{exists})
to encapsulate all internal structure. Therefore capturing similarities between
the differing levels of abstractions far outweigh their inevitable differences,

@@

\textbf{Contracting} \xspace \xspace Contracting is the definition, for each
software element, of the associated semantic properties. BON use a full
assertion mechanism, allowing analysts to specify not only the structure of
a system but also its semantics ( constraints and invariants of the expected results ).

@@

In VHDL-AMS any predefined (implicite) attribute 

@@

should be equal to the number of unknowns, i.e. \emph{free} and \emph{branch}
\emph{quantities}. For instance, when we reasoning about conservation of energy law,

@@

However, if our implementation does not satisfy conservation of energy law, 

@@

the \inv was broken and reestablished. 
It is important because we cannot patch a fabricated component once we started
massive production. \\
Another advantage of BON is an easily-readable, English-based textual notation.
The current IEEE standard VHDL-AMS language reference manual tries to define
VHDL-AMS as well as possible in a descriptive way, explaining the
semantics in English.\\

@@

\section{Refinement from VHDL-AMS to BON }
\label{sec:refVB}
The main theme of this article is the translation from VHDL-AMS to BON using 
refinement approach.
We will refine the VHDL-AMS code up to the formal BON, and from this 
specification we will generate an executable specification in the JML language.
For this purpose, we will demonstrate our approach in BON-JML fashion trought 
low-pass filter example.
\input{lowpassRC}
We can implement the last equation (see \autoref{fig:lowpassfig}) using the \texttt{'dot} 
implicite attribute of quantity. For this purpose we introduce relation 
\texttt{$s \rightarrow d/dt \rightarrow 'dot$} . The transformation looks as follows: \\
\begin{equation}
v_{in} = v_{out} + \tau_psv_{out} 
   \begin{array}[b]{c}                                                                                                                                    
      {\scriptscriptstyle s \rightarrow d/dt}  \\=                                                                                                                  
   \end{array} 
v_{out} + \tau_p\cfrac{dv_{out}}{dt}
\begin{array}[b]{c}                                                                                                                                    
      {\scriptscriptstyle d/dt \rightarrow } {\scriptscriptstyle 'dot} \\=                                                                                                                  
   \end{array}
  v_{in} = v_{out} + \tau_pv_{out}{'dot} 
\end{equation} 
\input{lowpass}
We have not yet said what specification and refinement are.
Let us introduce these therms first.\\ 
A specification of a program component is a contract that gives some constraints 
on how the component is to behave but leaves freedom for the implementator to 
decide how the actual behavior of the component is to be realized.
Specification involves \emph{choice} between a number of alternatives; this 
relationship is one-to-many. As we have shown in \autoref{tab:rescap}, corresponding 
informal specifications represents high level of abstraction derived from VHDL-AMS code.

A refinement represents the concept that can be understud as series of 
correctness-preserving transformations from general perspective to 
a precise level of detail. Accurately, if we compare two specifications,
\texttt{S} and \texttt{S'}, then we can conclude that the \texttt{S} 
is more abstract than \texttt{S'} if any condition that we can establish 
with the first specification can also be established by second. 
It means that "\texttt{S is \emph{refined} by S'}", 
and we denote this  as \texttt{S $\rightsquigarrow$ S'}.
Let say that the first informal BON specification is denoted by 
\texttt{S} (see \autoref{tab:rescap}), and second, which is given 
in Table2  is denoted by \texttt{S'}.
In this case, the refinement relation represents an \emph{isomorphism} 
and maps the following:
%=====================================================================
\section{Conclusion}

A conclusion.

@@

%======================================================================
%\appendix
%\newpage
%\section {APPENDIX}
%\input{static}
%\input{arith}
%\input{shift}
%\input{relation}
%\input{logic}
%\input{types}
%\input{assignment}
%\input{iscaltypeattr}
%\input{tolerance}
%\input{effort}
%\input{flow}
%\input{nature}
%\input{iscalnature}
%\input{iarrayattr}
%\input{scalnat}
%\input{iterminal}
%\input{terminal}
%\input{iquantity}
%\input{quantity}
%\input{quantityport}
%\input{terminalport}
%\input{signal}
%\input{signalattr}
%\input{wait}

%======================================================================

>>>>

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\ent}{entity\xspace}
\newcommand{\arch}{architecture\xspace}
\newcommand{\archs}{architectures\xspace}
\newcommand{\inv}{\emph{invariant}\xspace}
\newcommand{\undef}{\emph{undefined}\xspace}
\newcommand{\arcoss}{\emph{across}\xspace}
\newcommand{\through}{\emph{through}\xspace}

%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

\title{Refining from the VHDL-AMS Hardware Description Language 
to the BON High-level Specification Language}

@@

%======================================================================
\section{Introduction}
\label{sec:introduction}
The \ST sensor platform, represents heterogeneous 
collection of digital, analog and mixed signal hardware circuits. 
The complexity of our platform requires the need to strive for formal 
descriptions each component separately and  behavior of their 
complex interdependencies, in order to produce executable specification.
To make sure that the sensor platform works properly we need 
to translate the VHDL-AMS code into the specification, and to refine and 
verify this specification.
In other words, our aim is to establish formal link between behavior of a given 
sensor platform, and derived specification of components  in order to implement 
fully validated and verified \ST simulator.
For this purpose, we need notation and methodology 
which will be able to satisfy the requirements given below.\\ 
First, both of them, should be in sync with  VHDL-AMS language and reference 
manual which tries to define VHDL-AMS as well as possible in a descriptive way,
explaining the semantics in English.\\
Second, specification derived from the notation should  be easy to attach to 
the rest of the system architecture\xspace(driver, microprocessor emulator, 
test-benches e.t.c.).\\
Third, methodology must aid efforts on creation of target system 
correctness criteria, such that are independent of implementation.
It means that verification of simulator model should take place on specification 
using reasoning techniques provided for algebraic formalism before coding starts.\\
Fourth,a precise semantics should  provides the basis for
automated forward-backward engineering.\\
Managing these requirements, and insuring that the platform definition 
(constraints) are preserved and verified through all levels of 
abstraction is where one becomes aware of gaps in already 
used design methodologies.
In our opinion, the BON-JML approach is in line with requirements given above.
The authors will illustrate in this article how BON can represent a high
level analogue mapping notation and will further illustrate a refinement 
technique from VHDL-AMS to BON and JML.\\
This article provides three main contributions.
\begin{enumerate}
\item
 It provides a solution how to formally emulate
 piece of hardware using BON-JML approach; up to date BON and JML
 have been used mostly in the pure object oriented software construction.   
\item
It relates hardware description code and refinement technique.
It means that if a satisfactory VHDL-AMS code exists, then it can be simulated  from the 
BON (informal/formal) specification, and JML implementation by an 
appropriate sequence of refinements.
\item
It introduces \inv as a general concept of modeling hardware 
components behavior and their interactions.
To be more precisely, the behavioral specification of the \STS may 
be represented as a \inv on the signals at the circuit's ports and 
may be obtained by taking the conjunction of the \emph{invariants} 
that describe behaviors of the individual components separately.\\ 
\end{enumerate}
The rest of this article is organized as follows.
In \autoref{sec:vhdlams} we have  presented an overview of VHDL-AMS language.
\autoref{sec:choiceobon} defines  BON principles and explains the
reasons why we have decided to use BON method.
In \autoref{sec:mappingVB} we will show mapping between VHDL-AMS and BON. 
The central part of the our article is \autoref{sec:refVB}, in which
we will give practical aspect of refinement , applied on 
first order passive RC Low-Pass filter, in order to produce formal 
specification and software simulation.
In \autoref{sec:conclusion} the conclusions are given,
and directions of future studies are outlined. Finally, a comprehensive list 
of the mapping between BON and VHDL-AMS can be found in the appendix. \\ 
%=====================================================================

\section{VHDL-AMS}
\label{sec:vhdlams}
IEEE VHDL-AMS 1076.1 is the industry standard mixed-signal
high-level description language for electronic and multi-domain
systems. VHDL-AMS, as an superset of VHDL, supports modeling and
simulation of analog and mixed-signal systems. The main contribution
of VHDL-AMS is ability to describe the behavior of complex system
trought differential and algebraic equations (DAEs). For this purpose,
VHDL-AMS introduces the following capabilities and therms:

\begin{itemize}
\item
\emph{Terminals} represents phisical connection points or circuit nodes
of a network connectivity. They are declared to be of various
\emph{natures}, which represent different energy domains of a system.
Terminals hold no values; their only role is to facilitate the formation
of conservative equation sets that, in turn, constrain the associated
\emph{branch qualities}.
\item
The \emph{quantities} denote a waveform or a time series of values.
The behavior of the \emph{quantities} is given by the \emph{simultaneous
 statements}. They take values as a result of solving the set of simultaneous
ordinary differential and algebraic equations (DAEs). To simplify,
quantities can be understood as analog unknowns of (DAEs) that specify
analog behaviour. There are three kinds of quantity in VHDL-AMS: free,
branch and source quantities. A \emph{free quantity} can be used in
signal-flow modeling. A \emph{branch quantity} is used to model conservative energy
systems. A \emph{source quantity} is used for frequency and noise modeling.
\item
The \emph{simultaneous statements} creates one or more characteristic
equations that are solved by the dedicated simulation kernel a.k.a.
"analog solver", to model continuously valued behavior. 
\item
The \emph{procedural statements} or \emph{procedural} express analog behaviour
using sequential statements. Actually procedural describes analog behaviour
by computing new values for quantities from the current value of quantities.
\item
The \emph{break statement} is an construct which allows to
initialize the DAE system at the beginning of a transient
simulation and to mark discontinuities during such a transient
simulation. For any concurrent break statement there is an associated process.
A break statement allows restart of the analog kernel,
than overrides quantity values and executes concurrently with the analogue model.

@@

for object-oriented systems  which brings \emph{seamlessness},\xspace

@@

throughout the software life-cycle. Reversibility is the support for

@@

In VHDL-AMS, modelling represents an continuous top-down-bottom-up

@@

models consistent with the code. Keeping in sync various models, documentation

@@

\emph{Seamlessness} also plays an important role in relating behaviors at

@@

general behaviour (\inv).
 Therefore, capturing similarities between the differing levels of abstractions,

@@

\textbf{Contracting} \xspace \xspace Contract specification describe 
system components interaction, based on mutual obligations and benefits, 
and, for each software element, associated semantic properties. BON use a full
assertion mechanism, allowing analysts to specify both:\xspace (1) the \emph{structure} of
a system and (2)\xspace \emph{semantics} ( constraints and invariants).

@@

In VHDL-AMS any predefined (implicate) attribute 

@@

should be equal to the number of unknowns (\emph{quantities}). 
For instance, when we reasoning about the conservation of energy law,

@@

However, if our implementation does not satisfy the conservation of energy law, 

@@

the \inv was broken and reestablished. According to that we can conclude whether the 
quality of a component is satisfactory. Unlike in the case of software, where 
correction of an error is relatively inexpensive, an detected hardware error 
may require product replacement, which is associated with great expenses. 
In other words, we cannot patch a fabricated component once we started massive production. \\

@@

In this section, we briefly describe the mapping between VHDL-AMS and BON notation 
which is discussed in the points below.\\
\textbf{Structure} \xspace \xspace VHDL-AMS allows hierarchical structure 
modeling, meaning that the model subsystems can be developed independently.
As an top-level description, \lstinlinen|SYSTEM_CHART| in the BON notation  
can connect all the model subsystems  together to a model design.
In BON, model subsystem is denoted as the \lstinlinen|CLUSTER_CHART| whereas 
module is represented as the \lstinlinen|CLASS_CHART|.
Each module has a \texttt{port} interface: a set of \emph{inputs} and \emph{outputs} used for 
connecting modules with environment. The \texttt{port} section in 
\texttt{\ent}structure (input, output and generic values) are represented as 
a \emph{features} in the \lstinlinen|CLASS_CHART|.
The \lstinlinen|CLASS_CHART| \xspace can be equated with \ent-\arch 
structure in VHDL-AMS and the name of the \lstinlinen|CLASS_CHART|\xspace 
corresponds to the name of \texttt{\ent}in VHDL-AMS.\\ 
\textbf{Behavior} \xspace \xspace The module also contains an 
\texttt{\arch} implementation, which determines the way the module 
processes \emph{input}/\emph{output} signals and performs computations.
The \emph{constraint} section in the \lstinlinen|CLASS_CHART| 
contains the transfer function and holds the same information as 
the \texttt{\arch}section of the VHDL-AMS.\\ 
\textbf{Types and operators} \xspace \xspace There are many features of 
VHDL-AMS which are already mapped in BON by default, such as arithmetic, 
relational and logical operators and types like \xspace \texttt{integer},
\xspace \texttt{byte},\xspace\texttt{real},\xspace\texttt{character} and 
\xspace\texttt{boolean}.
Vector may be represented as \lstinlinen|SEQUENCE[TYPE]|, 
whereas record, whose elements are of heterogeneous types, can be mapped 
as \lstinlinen|SET| or \lstinlinen|TABLE|.
In BON, the \texttt{time} can be represented as the
\lstinlinen|UNIVERSAL_TIME|, in order to specify \emph{delays}. Actually 
time can be thought of as object with integer as a value and measurement 
units as a \xspace \lstinlinen|SEQUENCE| feature.     
In order to specify energy domain for nodes of circuits we have developed 
various standard \texttt{nature} templates for \texttt{terminals}.
We have introduced \xspace\lstinlinen|FREE|,\xspace \lstinlinen|BRANCH|
and  \xspace\lstinlinen|SOURCE| \space \lstinlinen|QUANTITY| objects, 
which are intended to describe signal-flow modeling, the 
conservation of energy low and frequency-noise related problems. 
There are also defined specifications for effort and 
flow domains, tolerance as well as appropriate contracts for 
scalar types(natures), array types(natures), 
terminals and quantity attributes.
Whereas the value assignment, in VHDL-AMS has the same purpose as in the BON,
the signal assignment, which schedules a new value to be applied to a 
signal later, is simulated in specification, but  denotational semantic
is not yet translated in the BON as well as for concurrency and 
the \texttt{wait} statement.

\section{Refinement from VHDL-AMS to BON }
\label{sec:refVB}
The main theme of this article is the translation from VHDL-AMS to BON using 
refinement approach.
We will refine the VHDL-AMS code up to the formal BON, and from this 
specification we will generate an executable specification in the JML language.
For this purpose, we will demonstrate our approach in BON-JML fashion trought 
low-pass filter example.
\input{lowpassRC}
According to equation given above (see \autoref{fig:lowpassfig}) 
we can produce VHDL-AMS \emph{simultaneous statement} using 
\texttt{$s \rightarrow d/dt \rightarrow 'dot$} relation.
The transformation looks as follows: \\
\begin{equation}
v_{in} = v_{out} + \tau_psv_{out} 
   \begin{array}[b]{c}                                                                                                                                    
      {\scriptscriptstyle s \rightarrow d/dt}  \\=                                                                                                                  
   \end{array} 
v_{out} + \tau_p\cfrac{dv_{out}}{dt}
\begin{array}[b]{c}                                                                                                                                    
      {\scriptscriptstyle d/dt \rightarrow } {\scriptscriptstyle 'dot} \\=                                                                                                                  
   \end{array}
  v_{in} = v_{out} + \tau_pv_{out}{'dot} 
\end{equation} 
\input{lowpass}
We have not yet said what specification and refinement are.
Let us introduce these terms first.\\ 
A specification of a program component is a contract that gives some constraints 
on how the component is to behave but leaves freedom for the implementator to 
decide how the actual behavior of the component is to be realized.
Specification involves \emph{choice} between a number of alternatives; this 
 relationship is one-to-many. As we have shown in \autoref{tab:rescap}, corresponding 
informal specifications represents high level of abstraction derived from VHDL-AMS code.

A refinement represents the concept that can be understud as series of 
correctness-preserving transformations from general perspective to 
a precise level of detail. Accurately, if we compare two specifications,
\texttt{S} and \texttt{S'}, then we can conclude that the \texttt{S} 
is more abstract than \texttt{S'} if any condition that we can establish 
with the first specification can also be established by second. 
It means that "\texttt{S is \emph{refined} by S'}", 
and we denote this  as \texttt{S $\rightsquigarrow$ S'}.
Let say that the first informal BON specification is denoted by 
\texttt{S} (see \autoref{tab:rescap}), and second, which is given in Table2  is denoted by \texttt{S'}.
In this case, the refinement relation represents an \emph{isomorphism} 
and maps the following:
%=====================================================================
\section{Conclusion}
\label{sec:conclusion}
The BON notation has originally been used for description of 
software models. However, after certain elaboration it can be used 
for description of hardware components. Practical utilization of the approach
in the project on mapping between VHDL-AMS and BON using refinement technique,
has demonstrated through low-pass filter example and shown that simulation
of component requires relatively little and inexpensive  efforts. Moreover, our article shown
that the development of the specification produced by the BON and translated 
into JML can be applied as refinement procedure: from VHDL-AMS to informal BON, 
next, from informal to more formal BON and finally, to JML specification. 
The BON support general software development and should be adapted for concrete
applications and language as VHDL-AMS. For this purpose we have developed various 
VHDL-AMS related types, operators and relations and we have defined appropriate 
specifications for all of them. However, the behavior of
\texttt{break} statement and  concurrency, for example, have not been translated 
yet in the BON notation. We have started a new phase of project named \emph{eBon} in which
the issues mentioned above, and creation of appropriate components and relations 
are main subject.

@@

%======================================================================
\appendix
\newpage
\section {APPENDIX}
\input{static}
\input{arith}
\input{shift}
\input{relation}
\input{logic}
\input{types}
\input{assignment}
\input{iscaltypeattr}
\input{tolerance}
\input{effort}
\input{flow}
\input{nature}
\input{iscalnature}
\input{iarrayattr}
\input{scalnat}
\input{iterminal}
\input{terminal}
\input{iquantity}
\input{quantity}
\input{quantityport}
\input{terminalport}
\input{signal}
\input{signalattr}
\input{wait}
\input{bitbon}
%======================================================================

### 2009-09-13 papers/BON_VHDL/static.tex
finalisation

\newcommand{\duc}{\emph{design units collection}\xspace}
\newcommand{\ducs}{\emph{design units collections}\xspace}
\newcommand{\du}{\emph{design unit}\xspace}
\begin{center}
\begin{tabular}{ c  c  c }
\multicolumn{3}{c}{\textbf{STATIC TYPES}}\\ 
\hline \hline
VHDL-AMS & BON & Description \\ 
\hline \hline
% first element
\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\ducs
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|SYSTEM_CHART|  
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
         \smallskip \smallskip
	VHDL-AMS allows hierarchical structure modeling, 
	meaning that subsistems (\ducs), can be developed 
        independently. As an top-level description 
        (informal/formal), \lstinlinen|SYSTEM_CHART|
        connect all the \ducs together 
        to a complete design. Actually \lstinlinen|SYSTEM_CHART|
        can be understood as VHDL-AMS package as a way of grouping 
        a collection of related declarations that serve a common 
        purpose.
        \smallskip \smallskip
\end{minipage}\\

@@

\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\duc
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|CLUSTER_CHART| 
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
      \smallskip \smallskip	 
      An  subsistem which represent \duc.
      \smallskip \smallskip
\end{minipage}\\

@@

\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\du
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|CLASS_CHART| 
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
      \smallskip \smallskip	 
      \lstinlinen|CLASS_CHART|  describes \du. 
      It can be identify with the primary unit (\ent) 
      and secondary unit (\arch) structure in VHDL-AMS. 
      The \lstinlinen|CLASS_CHART|'s name corresponds 
      to the name of the entity in VHDL-AMS.
      \smallskip \smallskip
\end{minipage}\\

>>>>

\begin{center}
\begin{tabular}{ c  c  c }
\multicolumn{3}{c}{\textbf{STATIC TYPES}}\\ 
\hline \hline
VHDL-AMS & BON & Description \\ 
\hline \hline
% first element
\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
\emph{model}
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|SYSTEM_CHART|  
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
         \smallskip \smallskip
	As an top-level description 
        (informal/formal), \lstinlinen|SYSTEM_CHART|
        connect all the model subsystems together 
        to a model.
        \smallskip \smallskip
\end{minipage}\\

@@

\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
model subsystem 
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|CLUSTER_CHART| 
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
      \smallskip \smallskip	 
      An  subsistem which represent module colleaction.
        VHDL-AMS allows hierarchical structure modeling, 
	meaning that subsystems (modules), can be developed 
        independently.
      \smallskip \smallskip
\end{minipage}\\

@@

\begin{minipage}[c]{2.4cm}
\smallskip \smallskip
\centering
modul
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{4.6cm}
\smallskip \smallskip
\centering
\lstinlinen|CLASS_CHART| 
\smallskip \smallskip
\end{minipage}
& 
\begin{minipage}[c]{6cm}
      \smallskip \smallskip	 
      \lstinlinen|CLASS_CHART|  describes module. 
      It can be identify with the primary unit (\ent) 
      and secondary unit (\arch) structure in VHDL-AMS. 
      The \lstinlinen|CLASS_CHART|'s name corresponds 
      to the name of the entity in VHDL-AMS.
      \smallskip \smallskip
\end{minipage}\\
